Bioverse: Origins of Life

### 2023-11-07 src/tex/ms.tex
write up prelim. conclusions

Our main findings are:
\begin{enumerate}
    \item Abiogenesis in the cyanosulfidic scenario strongly prefers late host star spectral types in a sample of transiting planets. Any potential biosignature detection on a planet around a star other than an M~dwarf would disvafor this scenario, and any \gls{ool} theory requiring extended periods of high \gls{NUV} irradiation.
\end{enumerate}

>>>>

Our main findings are:
\begin{enumerate}
    \item Models of the Origins of Life provide hypotheses that are testable with near-future exoplanet surveys.
    \item The required \gls{nuv} radiation in the cyanosulfidic scenario should lead to a correlation between past \gls{nuv} flux and current occurrence of biosignatures, both of which will soon be observationally accessible.
    \item The required sample size for detecting this correlation depends on the occurrence of life on temperate exoplanets, the distribution of host star spectral types in the sample, ...
        A direct imaging mission with the \gls{hwo} will require characterizing XXX planets ...
    \item Abiogenesis in the cyanosulfidic scenario strongly prefers late host star spectral types in a sample of transiting planets. Any potential biosignature detection on a planet around a star other than an M~dwarf would disvafor this scenario and any other \gls{ool} theory requiring extended periods of high \gls{nuv} irradiation.
\end{enumerate}
